\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-05-06 main.Rmd
updated description

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE,
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
read_chunk('src/main.R')
```

@@

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. The resulting plot is star glyphs---time series lines transformed in polar coordinates---embedded in the monthly calendar layout.

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days taking off and the overnight use for household 2 in mid January."}
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE,
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
read_chunk('scripts/main.R')
```

@@

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. The resulting plot is star glyphs [@chambers2017graphical], where time series lines are transformed in polar coordinates, embedded in the monthly calendar layout.

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays faceted by each household based on common scales. We can precisely tell each indidual's vacation days and the overnight use for household 2 in mid January."}
```

### 2019-05-06 main.tex
updated description

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on the data. The computation is similar to the one described in \citet{Wickham2012glyph}. The resulting plot is star glyphs---time series lines transformed in polar coordinates---embedded in the monthly calendar layout.

@@

\caption{Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days taking off and the overnight use for household 2 in mid January.}\label{fig:calendar-elec}
\end{figure}

>>>>

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on the data. The computation is similar to the one described in \citet{Wickham2012glyph}. The resulting plot is star glyphs \citep{chambers2017graphical}, where time series lines are transformed in polar coordinates, embedded in the monthly calendar layout.

@@

\caption{Calendar displays faceted by each household based on common scales. We can precisely tell each indidual's vacation days and the overnight use for household 2 in mid January.}\label{fig:calendar-elec}
\end{figure}
